% !TEX program = xelatex

\documentclass{chicv}

% optionally suppress printing the page number
\pagenumbering{gobble}

% GitLab social macro (mirrors chicv's \github with the fontawesome5 GitLab icon).
% In use while the GitHub account is suspended; repos are mirrored to GitLab.
\NewDocumentCommand{\gitlab}{ m o }{
    \faGitlab\IfNoValueTF{#2}{
        \underline{\href{#1}{#1}}
    }{
        \underline{\href{#2}{#1}}
    }
    \hspace{-20pt}
}

\begin{document}

%% basic personal info
\name{Yubo Huang}

\begin{basicinfo}
  \info{\email{yubo.huang@hotmail.com}}
  \info{\homepage{home}[https://huangyubo.gitlab.io/]}
  \info{\gitlab{huangyubo}[https://gitlab.com/huangyubo]}
  \info{\linkedinsquare{LinkedIn}[https://www.linkedin.com/in/yubo-huang-716530296]}
%  \info{\phone{+1 (236) 268-7977}}

\end{basicinfo}

\section{Education}
\cventry{Laurentian University}
  {Sep 2023 -- Jan 2025}
  [Master of Science in Computational Sciences]
  [Sudbury, Ontario, Canada]
  \begin{itemize}
    \item GPA 9.30/10
    \item Courses: Machine Learning/Deep Learning, Image Proc \& Comp Vision, etc.
  \end{itemize}

\cventry{Beijing University of Posts and Telecommunications}
  {Sep 2020 -- Jun 2023}
  [Master of Engineering in Materials Science and Engineering]
  [Beijing, China]
  \begin{itemize}
    \item Advisors: \href{https://teacher.bupt.edu.cn/hezhaofeng/en/index.htm}{\underline{Prof. Zhaofeng He}}, \href{https://scholar.google.com/citations?user=A0khpKYAAAAJ&hl=en}{\underline{Prof. Peipei Li}}, and \href{https://teacher.bupt.edu.cn/xiangliuyu/en/index.htm}{\underline{Prof. Liuyu Xiang}}.
    \item GPA 3.79/4
    \item Computer Science Courses: Java Programming, Advanced Operating Systems, Natural Language Processing and Applications, Data Mining Experiment, and AI Computing Systems
  \end{itemize}

\cventry{Beijing University of Posts and Telecommunications}
  {Sep 2016 -- Jun 2020}
  [Bachelor of Science in Applied Physics]
  [Beijing, China]
  \begin{itemize}
    \item GPA 76.86/100, Rank 43/55
    \item Computer Science Courses: The C Programming Language, Data Structures, Computational Physics and Practice, and Scientific Computing and Fortran
  \end{itemize}

\section{Publications}

\begin{itemize}
  \item \textbf{Yubo Huang}, Jia Wang, \href{https://teacher.bupt.edu.cn/lipeipei/en/index/241243/list/index.htm}{Peipei Li}, \href{https://teacher.bupt.edu.cn/xiangliuyu/en/lwcg/255396/list/index.htm}{Liuyu Xiang}, Peigang Li, and \href{https://teacher.bupt.edu.cn/hezhaofeng/en/lwcg/206617/list/index.htm}{Zhaofeng He}. \href{https://scholar.google.ca/scholar?q=Generative+Iris+Prior+Embedded+Transformer+for+Iris+Restoration.&hl=en&as_sdt=0&as_vis=1&oi=scholart}{Generative Iris Prior Embedded Transformer for Iris Restoration}. In 2023 IEEE International Conference on Multimedia and Expo (\textbf{ICME}), Brisbane, Australia, 2023 (\textbf{Oral}).
  % Hidden (was: Chinese-language publication). Uncomment to restore.
  % \item Jia Wang, \href{https://teacher.bupt.edu.cn/xiangliuyu/en/lwcg/255396/list/index.htm}{Liuyu Xiang}, \textbf{Yubo Huang}, \href{https://teacher.bupt.edu.cn/lipeipei/en/index/241243/list/index.htm}{Peipei Li}, Yufeng Xia, Qing Tian, and \href{https://teacher.bupt.edu.cn/hezhaofeng/en/lwcg/206617/list/index.htm}{Zhaofeng He}. \href{https://www.jsjkx.com/EN/Y2023/V50/I12/148}{Prior-guided Blind Iris Image Restoration Algorithm}. \href{https://www.jsjkx.com/EN/1002-137X/home.shtml}{Computer Science}, 2023, 50(12): 148-155. (in Chinese)
\end{itemize}

\section{Experience}

\cventry{{University of Alberta}}
  {Jun 2025 -- Present}
  [Research Intern, advised by Prof. Li Cheng][Edmonton, Alberta, Canada]
  \begin{itemize}
    \item Built a markerless multi-view smartphone rig and pipeline for \href{https://huangyubo.gitlab.io/motion-capture.html}{\underline{motion capture and 3D reconstruction}}, and reproduced a six-IMU motion capture method.
  \end{itemize}

\cventry{\href{https://github.com/DreamSoul-AI}{DreamSoul}}
  {Nov 2023 -- Present}
  [Research Volunteer, advised by \href{https://diaoenmao.com/}{\underline{Dr. Enmao Diao}}][Remote]
  \begin{itemize}
    \item \href{https://gitlab.com/huangyubo/Pixel-Pair-Encoding}{\underline{Pixel-Pair-Encoding}} Extends byte pair encoding from text to images.
    \item \href{https://gitlab.com/huangyubo/Neural-Data-Compression-with-Byte-Pair-Encoding}{\underline{Neural-Data-Compression-with-Byte-Pair-Encoding}} Integrates byte pair encoding into neural data compression.
    \item Neural-Data-Compression-Pipeline Builds a pipeline of major neural compression models for large-scale experiments.
  \end{itemize}

\cventry{Beijing University of Posts and Telecommunications}
  {Sep 2020 -- Aug 2021}
  [Teaching Assistant][Beijing, China]
  \begin{itemize}
    \item Instructed students in probability theory and mathematical statistics.
  \end{itemize}

\cventry{New Studios Media Group, Inc.}
  {Jan 2021 -- Mar 2021}
  [Test Intern][Beijing, China]
  \begin{itemize}
    \item Tested and documented software defects.
  \end{itemize}

\section{Skills}
\begin{compactlist}
  \item \textbf{Tech Skills}: 3D Computer Vision Engineering, Harness Engineering
  \item \textbf{English Language Proficiency}: Professional working proficiency (CELPIP 9)
\end{compactlist}

\section{Student Work}
\cventry{Beijing University of Posts and Telecommunications}
  {Sep 2018 -- Dec 2018}
  [Captain of School of Science and School of Cyberspace Security Basketball Team]
  [Beijing, China]

\end{document}
